GMSE: an R package for generalised management strategy evaluation

### 2018-04-30 notebook/ms/SI5.Rmd
Fix the procedure for reading it all in

>>>>

```{r}
newFL <- FLSR()
ssb.n <- read.csv("notebook/ms/data/SI5/nsher_ssb.csv")
rec.n <- read.csv("notebook/ms/data/SI5/nsher_rec.csv")
ssb.m <- as.matrix(ssb.n)
rec.m <- as.matrix(rec.n);
Frec.m <- FLQuant(ref.m, dimnames=list(age=1, year = 1960:2004))
Fssb.m <- FLQuant(ssb.m, dimnames=list(age=1, year = 1960:2004))
Frec.m@units <- "10^3"

newFL@rec <- Frec.m
newFL@ssb <- Fssb.m
```
